A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-15 6_validation.tex
figure comparison of even and inward distributed strategies

\paragraph{Inward distributed}
For example, we can choose 
$$M(n,d)_i = \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )$$
to distribute the discrepancy over the innermost $2N$ beads, and distribute most of it to the inner beads.
That way we limit the region of impact of the distributed strategy to a central region and have the nominal bead width $w_\text{pref}$ in regions farther away.
This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions. % and it forces most of the beads to have exactly the prefered width.
Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanial properties derived for prints using hte naive strategy will still hold approximately.

>>>>

\paragraph{Inward distributed}
For example, we can choose 
$$M(n,d)_i = \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )$$
to distribute the discrepancy over the innermost $2N$ beads, and distribute most of it to the inner beads.
See \cref{distributed_comparison}.
That way we limit the region of impact of the distributed strategy to a central region and have the nominal bead width $w_\text{pref}$ in regions farther away.
This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions. % and it forces most of the beads to have exactly the prefered width.
Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanial properties derived for prints using the naive strategy will still hold approximately.

\begin{figure}
\centering
\setlength{\figwidth}{.45\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=.8\columnwidth]{sources/validation/wedge_Distributed_pretty_evenly.png}
\caption{Evenly distributed}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=.8\columnwidth]{sources/validation/wedge_Distributed_pretty_inward.png}
\caption{Inward distributed}
\end{subfigure}
\caption{
Closeup of toolpaths generated with the distributed beading strategies for a large wedge shape.
}
\label{distributed_comparison}
\end{figure}
